%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Contents: Bibliography - Diplomarbeit, FH Regensburg          %
%                          11.03.2003                           %
%---------------------------------------------------------------%
%                         Literatur.tex                         %
%                      by Vorname Nachname                      %
%                         mail@mail.com                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{Sch}
  \textsc{A.Schroeder, T.Zimmermann, Rahul Premraj and A.Zeller}:
  \textsl{If Your Bug Database Could Talk...}.
 In Proceedings of the 5th International Symposium on Empirical Software Engineering, ISESE 2006.
 
 \bibitem{Nag}
  \textsc{N. Nagappan, T. Ball, and A. Zeller}:
  \textsl{Mining metrics to predict component failures}.
 In Proceedings of the International Conference on Software Engineering, ICSE 2006.
 
\bibitem{Sli}
  \textsc{J. Sliwerski, T. Zimmermann and A. Zeller}:
  \textsl{When do changes induce fixes}?
  In Proc. International Workshop on Mining
Software Repositories (MSR), St. Louis, Missouri, U.S., May
2005.
  
 \bibitem{Bet1}
  \textsc{N. Bettenburg, S. Just et al.}:
  \textsl{What Makes a Good Bug Report}?
  Universität des Saarlandes, Saarbrücken, Germany, March 2008. 
  
  \bibitem{Bet2}
  \textsc{N. Bettenburg, S. Just et al.}:
  \textsl{Quality of Bug Reports in Eclipse}.
  Proceedings of the 2007 OOPSLA Workshop on Eclipse Technology eXchange, ACM Press, New York, NY, USA, October 2007. 
  
  \bibitem{Tim1}
  \textsc{Tim Berners-Lee}:
  \textsl{Information Management: A Proposal}.
 CERN (March 1989, May 1990).
 
\bibitem{Tim2}
  \textsc{Tim Berners-Lee}:
  \textsl{First mention of HTML Tags on the www-talk mailing list}.
  World Wide Web Consortium. October 29, 1991.

\bibitem{JIRA}
  \textsc{Confluence.atlassian.com}:
  \textsl{JIRA 6.2 Release Notes}.
  Retrieved 18 April 2014.

\bibitem{XML}
  \textsc{Mounia Lalmas}:
  \textsl{XML Retrieval}.
  Morgan \& Claypool Publishers, August 08, 2009. 

\bibitem{XPath}
  \textsc{Randy Bergeron}:
  \textsl{XPath Retrieving Nodes from an XML Document}.
  SQL Server Magazine, October 31, 2000.  

\bibitem{CSV}
  \textsc{Y. Shafranovich}:
  \textsl{Common Format and MIME Type for CSV Files}.
  Network Working Group (RFC 4180), October, 2005.  
   
 %\bibitem{WikiOrth}
 % \verb|http://de.wikipedia.org/wiki/Orthogonale_Matrix|
 % \\
  
  
%\bibitem{SF}
 % \textsc{Schied, Alexander}:
 % \textsl{Finanzmathematik in stetiger Zeit}.
%  Skript, HWS 2010
 

%\bibitem{url_lexikon}
 % \verb|http://google.de|\\
  %google.de Suchmaschine

\end{thebibliography}
